Using Information Underlying Missing Data to Improve Estimation of NFL Field Goal Kicker Accuracy

### 2016-11-19 JaradNiemi_MwSAM2016.Rnw
Fix notation

\documentclass[handout]{beamer}

@@

\pause
A probit regression model for each kicker $k$ assumes 
\[ 
M_{ik} \ind Ber(\pi_{ik}) \quad \pi_{ik} = \Phi(\zeta_{ik}) \quad \zeta_{ik} = w_{ik}^\top \alpha_k.
\]

@@

The full model is 
\[ \begin{array}{rlrlrl}
Y_{ak} &\ind Ber(\theta_{ak}) & \theta_{ak}  &= \Phi\left(     x_{ak}^\top \beta_k \right) & \beta_k \ind N(\mu,\Sigma) \\
M_{ik} &\ind Ber(\pi_{ik})    & \pi_{ik}     &= \Phi\left(\omega_{ik}^\top \alpha\phantom{_k}  \right) \\
\omega_{ik} &= (w_{ik}, w_{ik}\Phi^{-1}(\theta_{ik}))
\end{array} \]
\pause
where 
\begin{itemize}
\item $x_{ak}$ is a set of explanatory variables that affect the probability of making a kick \pause and
\item $w_{ik}$ is a set of explanatory variables that affect the probability of taking a kick. 
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Informative missingness analysis}
<<informative_missing_data, fig.width=10, out.width="\\textwidth">>=
library(dplyr)

d = readr::read_csv("from_dennis/BdrawsIM.csv")[101:10100,-1]

@@

These slides are available at 
\begin{itemize}
\item {\scriptsize \url{https://github.com/jarad/MwSAM2016/raw/master/JaradNiemi_MwSAM2016.pdf}}
\item or on my website {\scriptsize \url{http://www.jarad.me/research/presentations.html}}.
\end{itemize}

>>>>

\documentclass{beamer}

@@

\pause
A probit regression model for each kicker $k$ assumes 
\[ 
A_{ik} \ind Ber(\pi_{ik}) \quad \pi_{ik} = \Phi(\zeta_{ik}) \quad \zeta_{ik} = w_{ik}^\top \alpha_k.
\]

@@

The full model is 
\[ \begin{array}{rlrlrl}
Y_{ak} &\ind Ber(\theta_{ak}) & \theta_{ak}  &= \Phi\left(     x_{ak}^\top \beta_k \right) & \beta_k \ind N(\mu,\Sigma) \\
A_{ik} &\ind Ber(\pi_{ik})    & \pi_{ik}     &= \Phi\left(\omega_{ik}^\top \alpha\phantom{_k}  \right) \\
\omega_{ik} &= (w_{ik}, w_{ik}\Phi^{-1}(\theta_{ik}))
\end{array} \]
\pause
where 
\begin{itemize}
\item $x_{ak}$ is a set of explanatory variables that affect the probability of making a kick \pause and
\item $w_{ik}$ is a set of explanatory variables that affect the probability of taking a kick. 
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Informative missingness analysis}
<<informative_missing_data>>=
library(dplyr)

d = suppressWarnings(readr::read_csv("from_dennis/BdrawsIM.csv")[101:10100,-1])

@@

These slides are available at 
\begin{itemize}
\item \url{}
\item or on my website \url{}.
\end{itemize}
